Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-08 method.tex
Removed a footnote
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@965 ccdd05d5-56c1-461a-bf98-85f6876523b4

Here we explore a method for reducing the computational cost of a \TD\ search
for compact binary coalescence.  We will give a truly zero-latency algorithm
that competes in terms of floating point operations per second with the
conventional \FD\ method, which requires a signficant latency in order to be
computationally cheap. Our method, \lloid{}\footnote{\lloid{} stands for
\emph{Low
Latency Online Inspiral Detection} and was a code name for this procedure
throughout development. Although the name doesn't carry any specific
information about the algorithm, it became known within the gravitational-wave
community and has stuck.}%
involves two transformations of the template waveforms that produce a set of
orthogonal filters with far fewer coefficients than the original templates.

>>>>

Here we explore a method for reducing the computational cost of a \TD\ search
for compact binary coalescence.  We will give a truly zero-latency algorithm
that competes in terms of floating point operations per second with the
conventional \FD\ method, which requires a signficant latency in order to be
computationally cheap. Our method, called \lloid{} (a backronym for
Low Latency Online Inspiral Detection),
involves two transformations of the template waveforms that produce a set of
orthogonal filters with far fewer coefficients than the original templates.
